Final Project

### 2020-11-30 chaloupka_sameshima_wallner_final_project.Rmd
ggridges
trying to use ggridges to show the by sequence position plot spread across different ridges. help if you can fix the error.

>>>>

# trying to use ggridges

library(ggridges)

new_data_never %>% 
  ggplot(aes(x = seq_pos2, y = mean_dwell_time, color = fractal_type)) +
  geom_density_ridges() +
  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
  scale_y_continuous(limits = c(0, 1.4)) +
  theme(legend.position = "none") +
  scale_color_viridis_d()
